Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-13 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:13	13:21:00	(Thu13.Aug)

MVDR is often able to improve image contrast and resolution compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, while the computational complexity of conventional beamformers are linear with the number of channels, O($M$), MVDR is at O($M^3$). This may discourage its use and in many cases make it infeasible. We have shown in previous studies that MVDR's complexity can be reduced, as well as accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014,Asen2013}, but there may be a way to avoid it altogether.

We propose a low complexity version of MVDR called the Low Complexity Adaptive (LCA) beamformer. This method applies a set of predefined windows and selects the one that is best able to suppress the noise. Using the LCA beamformer results in increased robustness and improved edge definition compared to the MV and DAS beamformers.

>>>>

In many cases MVDR can improve image contrast and resolution compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, the computational complexity of conventional beamformers are linear with the number of channels, O($M$), while MVDR is at O($M^3$). This may discourage its use and in many cases make it infeasible. We have shown in previous studies that MVDR's complexity can be reduced, as well as accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014,Asen2013}, but there is a way to avoid it altogether while achieving similar performance.

This method is called Low Complexity Adaptive (LCA) beamformer and was first proposed by Synnevåg et. al. in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar results to MVDR. It does this by applying a set of predefined windows and selects the one that is best able to suppress noise. Since it uses the same optimisation criterion as MVDR, it may be considered a version of MVDR with a reduced solution space. As we will demonstrate, this works well because MVDR needs

Using the LCA beamformer results in increased robustness and improved edge definition compared to the MV and DAS beamformers.
